---
title: "Continuous Model"
author: "me"
date: '2022-09-03'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Will try method but with a continuous model which combines both carrying capacities to produce a differential model of the growth each year. 
Start at low population, presume that growth rate will return to zero.


```{r}
library(tidyr)
library(dplyr)
library(tidyverse)
library(deSolve)
library(lattice)
library(igraph)
```



Recreating model found:
```{r}
PredpreyLV <- function(t,y,p){
  N1<-y[1]
  N2<-y[2]
  M1<-y[3]
  with(as.list(p),{
    mdN1dt<-r*m*N1*(1-C*((a*m*N1+b*m*M1)/Ks+(a*m*N1)/Kw1))
    mdN2dt<-r*m*N2*(1-C*((a*m*N2)/Ks+(a*m*N2+b*m*M1)/Kw2))
    mdM1dt<-r*m*M1*(1-C*((a*m*M1+b*m*N1)/Ks+(a*m*M1+b*m*N2)/Kw2))
    return(list(c(mdN1dt,mdN2dt,mdM1dt)))        
  })
}

r<-0.5;
a<-1;
b<-1;
C<-0.5;
m<-3
Ks<-2000;
Kw1<-500;
Kw2<-1700
p<-(c(r=r,a=a,b=b,C=C,m=m,Ks=Ks,Kw1=Kw1,Kw2=Kw2))
y0<-c(N1=25,N2=5,M1=20)
times<-seq(0,200,0.1)
LV.out<-ode(y=y0,times,PredpreyLV,p)
print(LV.out)

matplot(LV.out[,1],LV.out[,2:4],type="l",ylab="Population Size",xlab="Time")
```




Expand to 8 bins:

```{r}
PredpreyLV <- function(t,y,p){
  N1<-y[1]
  N2<-y[2]
  N3<-y[3]
  N4<-y[4]
  N5<-y[5]
  N6<-y[6]
  N7<-y[7]
  N8<-y[8]
  M1<-y[9]
  M2<-y[9]
  M3<-y[9]
  M4<-y[9]
  M5<-y[9]
  M6<-y[9]
  M7<-y[9]
  M8<-y[9]
  M9<-y[9]
  M10<-y[10]
  M11<-y[11]
  M12<-y[12]
  M13<-y[13]
  M14<-y[14]
  M15<-y[15]
  M16<-y[16]
  M17<-y[17]
  M18<-y[18]
  M19<-y[19]
  M20<-y[20]
  M21<-y[21]
  M22<-y[22]
  M23<-y[23]
  M24<-y[24]
  M25<-y[25]
  M26<-y[26]
  M27<-y[27]
  M28<-y[28]
  with(as.list(p),{
    mdN1dt<-r*m*N1*(1-C*((a*m*N1)/Ks+(a*m*(N1+M1+M2+M4+M7+M11+M16+M22))/Kw1))
    mdN2dt<-r*m*N2*(1-C*((a*m*(N2+M1))/Ks+(a*m*(N2+M3+M8+M12+M17+M23))/Kw2))
    mdN3dt<-r*m*N3*(1-C*((a*m*(N3+M2+M3))/Ks+(a*m*(N3+M6+M9+M13+M18+M24))/Kw3))
    mdN4dt<-r*m*N4*(1-C*((a*m*(N4+M4+M5+M6))/Ks+(a*m*(N4+M10+M14+M19+M25))/Kw4))
    mdN5dt<-r*m*N5*(1-C*((a*m*(N5+M7+M8+M9+M10))/Ks+(a*m*(N5+M15+M20+M26))/Kw5))
    mdN6dt<-r*m*N6*(1-C*((a*m*(N6+M11+M12+M13+M14+M15))/Ks+(a*m*(N6+M21+M27))/Kw6))
    mdN7dt<-r*m*N7*(1-C*((a*m*(N7+M16+M17+M18+M19+M20+M21))/Ks+(a*m*(N7+M28))/Kw7))
    mdN8dt<-r*m*N8*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M27+M28))/Ks+(a*m*N8)/Kw8))
    mdM1dt<-r*m*M1*(1-C*((a*m*(M1+N2))/Ks+(a*m*(M1+N1+M2+M4+M7+M11+M16+M22))/Kw1))
    mdM2dt<-r*m*M2*(1-C*((a*m*(M2+N3+M3))/Ks+(a*m*(M2+N1+M1+M4+M7+M11+M16+M22))/Kw1))
    mdM3dt<-r*m*M3*(1-C*((a*m*(M3+N3+M2))/Ks+(a*m**(M3+N2+M5+M8+M12+M17+M23))/Kw2))
    mdM4dt<-r*m*M4*(1-C*((a*m*(M4+N4+M5+M6))/Ks+(a*m*(M4+N1+M1+M2+M7+M11+M16+M22))/Kw1))
    mdM5dt<-r*m*M5*(1-C*((a*m*(M5+N4+M4+M6))/Ks+(a*m*(M5+N2+M3+M8+M12+M17+M23))/Kw2))
    mdM6dt<-r*m*M6*(1-C*((a*m*(M6+N4+M4+M5))/Ks+(a*m*(M6+N3+M9+M13+M18+M24))/Kw3))
    mdM7dt<-r*m*M7*(1-C*((a*m*(M7+N5+M8+M9+M10))/Ks+(a*m*(M1+N1+M2+M4+M7+M11+M16+M22))/Kw1))
    mdM8dt<-r*m*M8*(1-C*((a*m*(M8+N5+M7+M9+M10))/Ks+(a*m*(M5+N2+M3+M8+M12+M17+M23))/Kw2))
    mdM9dt<-r*m*M9*(1-C*((a*m*(M9+N5+M7+M8+M10))/Ks+(a*m*(M6+N3+M9+M13+M18+M24))/Kw3))
    mdM10dt<-r*m*M10*(1-C*((a*m*(M10+N5+M7+M8+M9))/Ks+(a*m*(M10+N4+M14+M19+M25))/Kw4))
    mdM11dt<-r*m*M11*(1-C*((a*m*(N6+M11+M12+M13+M14+M15))/Ks+(a*m*(N1+M1+M2+M4+M7+M11+M16+M22))/Kw1))
    mdM12dt<-r*m*M12*(1-C*((a*m*(N6+M11+M12+M13+M14+M15))/Ks+(a*m*(N2+M3+M8+M12+M17+M23))/Kw2))
    mdM13dt<-r*m*M13*(1-C*((a*m*(N6+M11+M12+M13+M14+M15))/Ks+(a*m*(N3+M6+M9+M13+M18+M24))/Kw3))
    mdM14dt<-r*m*M14*(1-C*((a*m*(N6+M11+M12+M13+M14+M15))/Ks+(a*m*(N4+M10+M14+M19+M25))/Kw4))
    mdM15dt<-r*m*M15*(1-C*((a*m*(N6+M11+M12+M13+M14+M15))/Ks+(a*m*(N5+M15+M20+M26))/Kw5))
    mdM16dt<-r*m*M16*(1-C*((a*m*(N7+M16+M17+M18+M19+M20+M21))/Ks+(a*m*(N1+M1+M2+M4+M7+M11+M16+M22))/Kw1))
    mdM17dt<-r*m*M17*(1-C*((a*m*(N7+M16+M17+M18+M19+M20+M21))/Ks+(a*m*(N2+M3+M8+M12+M17+M23))/Kw2))
    mdM18dt<-r*m*M18*(1-C*((a*m*(N7+M16+M17+M18+M19+M20+M21))/Ks+(a*m*(N3+M6+M9+M13+M18+M24))/Kw2))
    mdM19dt<-r*m*M19*(1-C*((a*m*(N7+M16+M17+M18+M19+M20+M21))/Ks+(a*m*(N4+M10+M14+M19+M25))/Kw2))
    mdM20dt<-r*m*M20*(1-C*((a*m*(N7+M16+M17+M18+M19+M20+M21))/Ks+(a*m*(N5+M15+M20+M26))/Kw2))
    mdM21dt<-r*m*M21*(1-C*((a*m*(N7+M16+M17+M18+M19+M20+M21))/Ks+(a*m*(N6+M21+M27))/Kw2))
    mdM22dt<-r*m*M22*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M27+M28))/Ks+(a*m*(N1+M1+M2+M4+M7+M11+M16+M22))/Kw2))
    mdM23dt<-r*m*M23*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M27+M28))/Ks+(a*m*(N2+M3+M8+M12+M17+M23))/Kw2))
    mdM24dt<-r*m*M24*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M27+M28))/Ks+(a*m*(N3+M6+M9+M13+M18+M24))/Kw2))
    mdM25dt<-r*m*M25*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M27+M28))/Ks+(a*m*(N4+M10+M14+M19+M25))/Kw2))
    mdM26dt<-r*m*M26*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M27+M28))/Ks+(a*m*(N5+M15+M20+M26))/Kw2))
    mdM27dt<-r*m*M27*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M27+M28))/Ks+(a*m*(N6+M21+M27))/Kw2))
    mdM28dt<-r*m*M28*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M27+M28))/Ks+(a*m*(N7+M28))/Kw2))
    return(list(c(mdN1dt,mdN2dt,mdN3dt,mdN4dt,mdN5dt,mdN6dt,mdN7dt,mdN8dt,mdM1dt,mdM2dt,mdM3dt,mdM4dt,mdM5dt,mdM6dt,mdM7dt,mdM8dt,mdM9dt,mdM10dt,mdM11dt,mdM12dt,mdM13dt,mdM14dt,mdM15dt,mdM16dt,mdM17dt,mdM18dt,mdM19dt,mdM20dt,mdM21dt,mdM22dt,mdM23dt,mdM24dt,mdM25dt,mdM26dt,mdM27dt,mdM28dt)))
  })
}

r<-0.5;
a<-1;
b<-1;
C<-0.5;
m<-3
Ks<-2000;
Kw1<-1800;
Kw2<-1600
Kw3<-1400
Kw4<-1200
Kw5<-1000
Kw6<-800
Kw7<-700
Kw8<-600
p<-(c(r=r,a=a,b=b,C=C,m=m,Ks=Ks,Kw1=Kw1,Kw2=Kw2,Kw3=Kw3,Kw4=Kw4,Kw5=Kw5,Kw6=Kw6,Kw7=Kw7,Kw8=Kw8))
y0<-c(N1=25,N2=5,N3=10,N4=10,N5=10,N6=10,N7=10,N8=10,M1=20,M2=10,M3=0,M4=10,M5=10,M6=10,M7=10,M8=10,M9=10,M10=10,M11=0,M12=10,M13=10,M14=10,M15=10,M16=10,M17=10,M18=10,M19=0,M20=10,M21=10,M22=10,M23=10,M24=10,M25=10,M26=10,M27=0,M28=10)
times<-seq(0,200,1)
LV.out<-ode(y=y0,times,PredpreyLV,p)
print(LV.out)

matplot(LV.out[,1],LV.out[,2:28],type="l",ylab="Population Size",xlab="Time")
```
Remade removing M3, M11, M19, M27
```{r}
PredpreyLV <- function(t,y,p){
  N1<-y[1]
  N2<-y[2]
  N3<-y[3]
  N4<-y[4]
  N5<-y[5]
  N6<-y[6]
  N7<-y[7]
  N8<-y[8]
  M1<-y[9]
  M2<-y[10]
  M4<-y[11]
  M5<-y[12]
  M6<-y[13]
  M7<-y[14]
  M8<-y[15]
  M9<-y[16]
  M10<-y[17]
  M12<-y[18]
  M13<-y[19]
  M14<-y[20]
  M15<-y[21]
  M16<-y[22]
  M17<-y[23]
  M18<-y[24]
  M20<-y[25]
  M21<-y[26]
  M22<-y[27]
  M23<-y[28]
  M24<-y[29]
  M25<-y[30]
  M26<-y[31]
  M28<-y[32]
  with(as.list(p),{
    mdN1dt<-r*m*N1*(1-C*((a*m*N1)/Ks1+(a*m*(N1+M1+M2+M4+M7+M16+M22))/Kw1))
    mdN2dt<-r*m*N2*(1-C*((a*m*(N2+M1))/Ks2+(a*m*(N2+M8+M12+M17+M23))/Kw2))
    mdN3dt<-r*m*N3*(1-C*((a*m*(N3+M2))/Ks3+(a*m*(N3+M6+M9+M13+M18+M24))/Kw3))
    mdN4dt<-r*m*N4*(1-C*((a*m*(N4+M4+M5+M6))/Ks4+(a*m*(N4+M10+M14+M25))/Kw4))
    mdN5dt<-r*m*N5*(1-C*((a*m*(N5+M7+M8+M9+M10))/Ks5+(a*m*(N5+M15+M20+M26))/Kw5))
    mdN6dt<-r*m*N6*(1-C*((a*m*(N6+M12+M13+M14+M15))/Ks6+(a*m*(N6+M21))/Kw6))
    mdN7dt<-r*m*N7*(1-C*((a*m*(N7+M16+M17+M18+M20+M21))/Ks7+(a*m*(N7+M28))/Kw7))
    mdN8dt<-r*m*N8*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M28))/Ks8+(a*m*N8)/Kw8))
    mdM1dt<-r*m*M1*(1-C*((a*m*(M1+N2))/Ks2+(a*m*(M1+N1+M2+M4+M7+M16+M22))/Kw1))
    mdM2dt<-r*m*M2*(1-C*((a*m*(M2+N3))/Ks3+(a*m*(M2+N1+M1+M4+M7+M16+M22))/Kw1))
    mdM4dt<-r*m*M4*(1-C*((a*m*(M4+N4+M5+M6))/Ks4+(a*m*(M4+N1+M1+M2+M7+M16+M22))/Kw1))
    mdM5dt<-r*m*M5*(1-C*((a*m*(M5+N4+M4+M6))/Ks4+(a*m*(M5+N2+M8+M12+M17+M23))/Kw2))
    mdM6dt<-r*m*M6*(1-C*((a*m*(M6+N4+M4+M5))/Ks4+(a*m*(M6+N3+M9+M13+M18+M24))/Kw3))
    mdM7dt<-r*m*M7*(1-C*((a*m*(M7+N5+M8+M9+M10))/Ks5+(a*m*(M1+N1+M2+M4+M7+M16+M22))/Kw1))
    mdM8dt<-r*m*M8*(1-C*((a*m*(M8+N5+M7+M9+M10))/Ks5+(a*m*(M5+N2+M8+M12+M17+M23))/Kw2))
    mdM9dt<-r*m*M9*(1-C*((a*m*(M9+N5+M7+M8+M10))/Ks5+(a*m*(M6+N3+M9+M13+M18+M24))/Kw3))
    mdM10dt<-r*m*M10*(1-C*((a*m*(M10+N5+M7+M8+M9))/Ks5+(a*m*(M10+N4+M14+M25))/Kw4))
    mdM12dt<-r*m*M12*(1-C*((a*m*(N6+M12+M13+M14+M15))/Ks6+(a*m*(N2+M8+M12+M17+M23))/Kw2))
    mdM13dt<-r*m*M13*(1-C*((a*m*(N6+M12+M13+M14+M15))/Ks6+(a*m*(N3+M6+M9+M13+M18+M24))/Kw3))
    mdM14dt<-r*m*M14*(1-C*((a*m*(N6+M12+M13+M14+M15))/Ks6+(a*m*(N4+M10+M14+M25))/Kw4))
    mdM15dt<-r*m*M15*(1-C*((a*m*(N6+M12+M13+M14+M15))/Ks6+(a*m*(N5+M15+M20+M26))/Kw5))
    mdM16dt<-r*m*M16*(1-C*((a*m*(N7+M16+M17+M18+M20+M21))/Ks7+(a*m*(N1+M1+M2+M4+M7+M16+M22))/Kw1))
    mdM17dt<-r*m*M17*(1-C*((a*m*(N7+M16+M17+M18+M20+M21))/Ks7+(a*m*(N2+M8+M12+M17+M23))/Kw2))
    mdM18dt<-r*m*M18*(1-C*((a*m*(N7+M16+M17+M18+M20+M21))/Ks7+(a*m*(N3+M6+M9+M13+M18+M24))/Kw2))
    mdM20dt<-r*m*M20*(1-C*((a*m*(N7+M16+M17+M18+M20+M21))/Ks7+(a*m*(N5+M15+M20+M26))/Kw2))
    mdM21dt<-r*m*M21*(1-C*((a*m*(N7+M16+M17+M18+M20+M21))/Ks7+(a*m*(N6+M21))/Kw2))
    mdM22dt<-r*m*M22*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M28))/Ks8+(a*m*(N1+M1+M2+M4+M7+M16+M22))/Kw2))
    mdM23dt<-r*m*M23*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M28))/Ks8+(a*m*(N2+M8+M12+M17+M23))/Kw2))
    mdM24dt<-r*m*M24*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M28))/Ks8+(a*m*(N3+M6+M9+M13+M18+M24))/Kw2))
    mdM25dt<-r*m*M25*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M28))/Ks8+(a*m*(N4+M10+M14+M25))/Kw2))
    mdM26dt<-r*m*M26*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M28))/Ks8+(a*m*(N5+M15+M20+M26))/Kw2))
    mdM28dt<-r*m*M28*(1-C*((a*m*(N8+M22+M23+M24+M25+M26+M28))/Ks8+(a*m*(N7+M28))/Kw2))
    return(list(c(mdN1dt,mdN2dt,mdN3dt,mdN4dt,mdN5dt,mdN6dt,mdN7dt,mdN8dt,mdM1dt,mdM2dt,mdM4dt,mdM5dt,mdM6dt,mdM7dt,mdM8dt,mdM9dt,mdM10dt,mdM12dt,mdM13dt,mdM14dt,mdM15dt,mdM16dt,mdM17dt,mdM18dt,mdM20dt,mdM21dt,mdM22dt,mdM23dt,mdM24dt,mdM25dt,mdM26dt,mdM28dt)))
  })
}

r<-0.5;
a<-1;
b<-1;
C<-0.5;
m<-3
Ks1<-2500;
Ks2<-2400;
Ks3<-2300;
Ks4<-2200;
Ks5<-2100
Ks6<-1800
Ks7<-1500
Ks8<-1200
Kw1<-1800;
Kw2<-1600
Kw3<-1400
Kw4<-1200
Kw5<-1000
Kw6<-800
Kw7<-700
Kw8<-600
p<-(c(r=r,a=a,b=b,C=C,m=m,Ks1=Ks1,Ks2=Ks2,Ks3=Ks3,Ks4=Ks4,Ks5=Ks5,Ks6=Ks6,Ks7=Ks7,Ks8=Ks8,Kw1=Kw1,Kw2=Kw2,Kw3=Kw3,Kw4=Kw4,Kw5=Kw5,Kw6=Kw6,Kw7=Kw7,Kw8=Kw8))
y0<-c(N1=25,N2=5,N3=10,N4=10,N5=10,N6=10,N7=10,N8=10,M1=20,M2=10,M4=10,M5=10,M6=10,M7=10,M8=10,M9=10,M10=10,M12=10,M13=10,M14=10,M15=10,M16=10,M17=10,M18=10,M20=10,M21=10,M22=10,M23=10,M24=10,M25=10,M26=10,M28=10)
times<-seq(0,200,1)
LV.out<-ode(y=y0,times,PredpreyLV,p)
print(LV.out)

matplot(LV.out[,1],LV.out[,2:33],type="l",ylab="Population Size",xlab="Time (yrs)")
```



Testing bipartite graph
```{r}
library(igraph)

set.seed(123)

# generate random bipartite graph.
g <- sample_bipartite(10, 5, p=.4)
g

# check the type attribute:
V(g)$type

# define color and shape mappings.
col <- c("steelblue", "orange")
shape <- c("circle", "square")

plot(g,
  vertex.color = col[as.numeric(V(g)$type)+1],
  vertex.shape = shape[as.numeric(V(g)$type)+1]
)
```


```{r}
set.seed(123)
V1 <- sample(LETTERS[1:10], size = 10, replace = TRUE)
V2 <- sample(1:10, size = 10, replace = TRUE)

d <- data.frame(V1 = V1, V2 = V2, weights = runif(10))
d

g <- graph_from_data_frame(d, directed = FALSE)
V(g)$label <- V(g)$name # set labels.

# create a graph connecting central node FOO to each V2.
e <- expand.grid(V2 = unique(d$V2), V2 = "FOO")
e

g2 <- graph.data.frame(e, directed = FALSE)

# join the two graphs.
g <- g + g2

# set type.
V(g)$type <- 1
V(g)[name %in% 1:10]$type <- 2
V(g)[name %in% "FOO"]$type <- 3

V(g)$type

col <- c("steelblue", "orange", "green")
shape <- c("circle", "square", "circle")

plot(g,
     vertex.color = col[V(g)$type],
     vertex.shape = shape[V(g)$type],
     edge.width = E(g)$weights * 5 # optional, plot edges width proportional to weights.
)
```


produce smaller bipartite graph
```{r}
A <- matrix(c(30,0,0,25,20,0,15,10,5),byrow = T, nrow = 3, ncol = 3)
rownames(A) <- c("1s","2s","3s")
colnames(A) <- c("1w","2w","3w")
print(A)

g <- graph.incidence(A, weighted = T)
g

V(g)$type

V(g)$color <- V(g)$type
V(g)$color=gsub("FALSE","red",V(g)$color)
V(g)$color=gsub("TRUE","blue",V(g)$color)
plot(g, edge.color="green3",edge.width=E(g)$weight/2, layout=layout_as_bipartite)
```

Trial of test bipartite graph using data from model:
```{r}
A <- matrix(c(LV.out[201,2],0,0,0,0,0,0,0,LV.out[201,10],LV.out[201,3],0,0,0,0,0,0,LV.out[201,11],0,LV.out[201,4],0,0,0,0,0,LV.out[201,12],LV.out[201,13],LV.out[201,14],LV.out[201,5],0,0,0,0,LV.out[201,15],LV.out[201,16],LV.out[201,17],LV.out[201,18],LV.out[201,6],0,0,0,0,LV.out[201,19],LV.out[201,20],LV.out[201,21],LV.out[201,22],LV.out[201,7],0,0,LV.out[201,23],LV.out[201,24],LV.out[201,25],0,LV.out[201,26],LV.out[201,27],LV.out[201,8],0,LV.out[201,28],LV.out[201,29],LV.out[201,30],LV.out[201,31],LV.out[201,32],LV.out[201,33],0,LV.out[201,9]),byrow = T, nrow = 8, ncol = 8)
rownames(A) <- c("1s","2s","3s","4s","5s","6s","7s","8s")
colnames(A) <- c("1w","2w","3w","4w","5w","6w","7w","8w")
print(A)

g <- graph.incidence(A, weighted = T)
g

V(g)$type

par(mar = c(0.1, 0.1, 0.1, 0.1))  

l <- layout.bipartite(g)
V(g)$color <- V(g)$type
V(g)$color=gsub("FALSE","red",V(g)$color)
V(g)$color=gsub("TRUE","blue",V(g)$color)
plot(g, edge.color="green3",edge.width=E(g)$weight/60,vertex.size=c(Ks1,Ks2,Ks3,Ks4,Ks5,Ks6,Ks7,Ks8,Kw1,Kw2,Kw3,Kw4,Kw5,Kw6,Kw7,Kw8)/80, layout=l[, c(2,1)])
```


