---
title: "Final Model"
author: "me"
date: '2022-08-09'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyr)
```

Taking the previous 4 bin model we shall add 4 extra functions for external migrants travelling to each patch. These will all come from the same breeding patch, B. In total we will have 11 pairs of equations.
```{r}
Res1summer <- function(r,K1s,initialR1){
  initialR1*(1+r*(1-(initialR1/K1s)))
}
Res1winter <- function(r,K1w,initialR1,alpha,initialAM2,beta,initialM1){
  initialR1*(1+r*(1-((initialR1+alpha*initialAM2+beta*initialM1)/K1w)))
}
Res2summer <- function(r,K2s,initialR2,alpha,initialAM2)
  initialR2*(1+r*(1-(initialR2+alpha*initialAM2)/K2s))

Res2winter <- function(r,K2w,initialR2,alpha,initialAM3,beta,initialM2)
  initialR2*(1+r*(1-((initialR2+alpha*initialAM3+beta*initialM2)/K2w)))

Res3summer <- function(r,K3s,initialR3,alpha,initialAM3){
  initialR3*(1+r*(1-(initialR3+alpha*initialAM3)/K3s))
}
Res3winter <- function(r,K3w,initialR3,alpha,initialAM4,beta,initialM3){
  initialR3*(1+r*(1-((initialR3+alpha*initialAM4+beta*initialM3)/K3w)))
}
Res4summer <- function(r,K4s,initialR4,alpha,initialAM4)
  initialR4*(1+r*(1-(initialR4+alpha*initialAM4)/K4s))

Res4winter <- function(r,K4w,initialR4,beta,initialM4)
  initialR4*(1+r*(1-((initialR4+beta*initialM4)/K4w)))

Alt_Migrant2summer <- function(r,K2s,initialAM2,sigma,initialR2)
  initialAM2*(1+r*(1-(initialAM2+sigma*initialR2)/K2s))

Alt_Migrant2winter <- function(r,K1w,initialAM2,sigma,initialR1,beta,initialM1)
  initialAM2*(1+r*(1-((initialAM2+sigma*initialR1+beta*initialM1)/K1w)))

Alt_Migrant3summer <- function(r,K3s,initialAM3,sigma,initialR3)
  initialAM3*(1+r*(1-(initialAM3+sigma*initialR3)/K3s))

Alt_Migrant3winter <- function(r,K2w,initialAM3,sigma,initialR2,beta,initialM2)
  initialAM3*(1+r*(1-((initialAM3+sigma*initialR2+beta*initialM2)/K2w)))

Alt_Migrant4summer <- function(r,K4s,initialAM4,sigma,initialR4)
  initialAM4*(1+r*(1-(initialAM4+sigma*initialR4)/K4s))

Alt_Migrant4winter <- function(r,K3w,initialAM4,sigma,initialR3,beta,initialM3)
  initialAM4*(1+r*(1-(initialAM4+sigma*initialR3+beta*initialM3)/K3w))

Migrant1summer <- function(r,B,initialM1,beta,initialM2,initialM3,initialM4)
  initialM1*(1+r*(1-(initialM1+beta*(initialM2+initialM3+initialM4))/B))

Migrant1winter <- function(r,K1w,initialM1,alpha,initialAM2,sigma,initialR1)
  initialM1*(1+r*(1-((initialM1+alpha*initialAM2+sigma*initialR1)/K1w)))

Migrant2summer <- function(r,B,initialM2,beta,initialM1,initialM3,initialM4)
  initialM2*(1+r*(1-(initialM2+beta*(initialM1+initialM3+initialM4))/B))

Migrant2winter <- function(r,K2w,initialM2,alpha,initialAM3,sigma,initialR2)
  initialM2*(1+r*(1-((initialM2+alpha*initialAM3+sigma*initialR2)/K2w)))

Migrant3summer <- function(r,B,initialM3,beta,initialM1,initialM2,initialM4)
  initialM3*(1+r*(1-(initialM3+beta*(initialM1+initialM2+initialM4))/B))

Migrant3winter <- function(r,K3w,initialM3,alpha,initialAM4,sigma,initialR3)
  initialM3*(1+r*(1-((initialM3+alpha*initialAM4+sigma*initialR3)/K3w)))

Migrant4summer <- function(r,B,initialM4,beta,initialM1,initialM2,initialM3)
  initialM4*(1+r*(1-(initialM4+beta*(initialM1+initialM2+initialM3))/B))

Migrant4winter <- function(r,K4w,initialM4,sigma,initialR4)
  initialM4*(1+r*(1-(initialM4+sigma*initialR4)/K4w))

```


```{r}
populationres1 = 9538
populationres2 = 2794
populationres3 = 1413
populationres4 = 140
populationaltmig2 = 4169
populationaltmig3 = 1909
populationaltmig4 = 209
populationmig1 = 9127
populationmig2 = 3687
populationmig3 = 1876
populationmig4 = 203
year_vector<-c()
populationres1_vector<-c()
populationres2_vector<-c()
populationres3_vector<-c()
populationres4_vector<-c()
populationaltmig2_vector<-c()
populationaltmig3_vector<-c()
populationaltmig4_vector<-c()
populationmig1_vector<-c()
populationmig2_vector<-c()
populationmig3_vector<-c()
populationmig4_vector<-c()
for (year in (1:20)/2) {
  if ((year %% 1) ==0){
  populationres1<-Res1summer(r=0.7,initialR1=populationres1,K1s=12689)
  populationres2<-Res2summer(r=0.7,initialR2=populationres2,K2s=2525,alpha=0.2,initialAM2=populationaltmig2)
  populationres3<-Res3summer(r=0.7,initialR3=populationres3,K3s=2175,alpha=0.2,initialAM3 = populationaltmig3)
  populationres4<-Res4summer(r=0.7,initialR4=populationres4,K4s=226,alpha=0.2,initialAM4 = populationaltmig4)
  populationaltmig2<-Alt_Migrant2summer(r=0.7,initialAM2=populationaltmig2,K2s=2525,sigma = 0.2,initialR2 = populationres2)
  populationaltmig3<-Alt_Migrant3summer(r=0.7,initialAM3=populationaltmig3,K3s=2175,sigma = 0.2,initialR3 = populationres3)
  populationaltmig4<-Alt_Migrant4summer(r=0.7,initialAM4=populationaltmig4,K4s=226,sigma = 0.2,initialR4 = populationres4)
  populationmig1<-Migrant1summer(r=0.7,initialM1=populationmig1,B=10000,beta = 0.4,initialM2 = populationmig2,initialM3 = populationmig3,initialM4 = populationmig4)
  populationmig2<-Migrant2summer(r=0.7,initialM2=populationmig2,B=10000,beta = 0.4,initialM1 = populationmig1,initialM3 = populationmig3,initialM4 = populationmig4)
  populationmig3<-Migrant3summer(r=0.7,initialM3=populationmig3,B=10000,beta = 0.4,initialM1 = populationmig1,initialM2 = populationmig2,initialM4 = populationmig4)
  populationmig4<-Migrant4summer(r=0.7,initialM4=populationmig4,B=10000,beta = 0.4,initialM1 = populationmig1,initialM2 = populationmig2,initialM3 = populationmig3)
  }
  else {
  populationres1<-Res1winter(r=0.7,initialR1=populationres1, alpha=0.2,initialAM2 = populationaltmig2, beta = 0.2, initialM1 = populationmig1, K1w=9215)
  populationres2<-Res2winter(r=0.7,initialR2=populationres2, alpha=0.2, initialAM3 = populationaltmig3, beta=0.2, initialM2 = populationmig2,K2w=1885)
  populationres3<-Res3winter(r=0.7,initialR3=populationres3, alpha=0.2, initialAM4 = populationaltmig4, beta=0.2, initialM3 = populationmig3,K3w=1485)
  populationres4<-Res4winter(r=0.7,initialR4=populationres4, beta=0.2, initialM4 = populationmig4, K4w=153)
  populationaltmig2<-Alt_Migrant2winter(r=0.7, initialAM2 = populationaltmig2, sigma=0.2, initialR1=populationres1, beta=0.2, initialM1 = populationmig1, K1w=9215)
  populationaltmig3<-Alt_Migrant3winter(r=0.7, initialAM3 = populationaltmig3, sigma=0.2, initialR2=populationres2, beta=0.2, initialM2=populationmig2, K2w=1885)
  populationaltmig4<-Alt_Migrant4winter(r=0.7, initialAM4 = populationaltmig4, sigma=0.2, initialR3=populationres3, beta=0.2, initialM3 = populationmig3, K3w=1485)
  populationmig1<-Migrant1winter(r=0.7, initialM1 = populationmig1, alpha=0.4, initialAM2 = populationaltmig2, sigma=0.4, initialR1=populationres1, K1w=9215)
  populationmig2<-Migrant2winter(r=0.7, initialM2 = populationmig2, alpha=0.4, initialAM3 = populationaltmig3, sigma=0.4, initialR2=populationres2,K2w=1885)
  populationmig3<-Migrant3winter(r=0.7, initialM3 = populationmig3, alpha=0.4, initialAM4 = populationaltmig4, sigma=0.4, initialR3 = populationres3, K3w=1485)
  populationmig4<-Migrant4winter(r=0.7, initialM4 = populationmig4, sigma=0.4, initialR4=populationres4, K4w=153)
  }
  year_vector<-append(year_vector,year)
  populationres1_vector<-append(populationres1_vector,populationres1)
  populationres2_vector<-append(populationres2_vector,populationres2)
  populationres3_vector<-append(populationres3_vector,populationres3)
  populationres4_vector<-append(populationres4_vector,populationres4)
  populationaltmig2_vector<-append(populationaltmig2_vector,populationaltmig2)
  populationaltmig3_vector<-append(populationaltmig3_vector,populationaltmig3)
  populationaltmig4_vector<-append(populationaltmig4_vector,populationaltmig4)
  populationmig1_vector<-append(populationmig1_vector,populationmig1)
  populationmig2_vector<-append(populationmig2_vector,populationmig2)
  populationmig3_vector<-append(populationmig3_vector,populationmig3)
  populationmig4_vector<-append(populationmig4_vector,populationmig4)
}

df<-data.frame( 
  Year = year_vector,
  Population_Resident1 = populationres1_vector,
  Population_Resident2 = populationres2_vector,
  Population_Resident3 = populationres3_vector,
  Population_Resident4 = populationres4_vector,
  Population_Alt_Migrant2 = populationaltmig2_vector,
  Population_Alt_Migrant3 = populationaltmig3_vector,
  Population_Alt_Migrant4 = populationaltmig4_vector,
  Population_Migrant1 = populationmig1_vector,
  Population_Migrant2 = populationmig2_vector,
  Population_Migrant3 = populationmig3_vector,
  Population_Migrant4 = populationmig4_vector) 

df_long<-gather(df,key="key",value="Population","Population_Resident1","Population_Resident2","Population_Resident3","Population_Resident4","Population_Alt_Migrant2","Population_Alt_Migrant3","Population_Alt_Migrant4","Population_Migrant1","Population_Migrant2","Population_Migrant3","Population_Migrant4")

final_model1<-ggplot(df_long,aes(x=Year, y=Population, colour=key)) +
   geom_line() +ggtitle("Four Resident species + three alitudinal migratory + four external migratory")
print(df)
print(df_long)
print(final_model1)
ggsave("myplot8.png", plot = final_model1,width = 10,height=6)
```

Model seems stable, and shows the levels we would expect. Small perturbations cause drops in numbers but not extinction, which is also a good sign.

It also shows the expected result whereby populations have a drastic drop then level out when the resources are decreased.

```{r}
df_combined<-data.frame( 
  Year = year_vector,
  Population_Resident = populationres1_vector + populationres2_vector + populationres3_vector + populationres4_vector +populationaltmig2_vector + populationaltmig3_vector + populationaltmig4_vector,
  Population_Migrant = populationmig1_vector+ populationmig2_vector + populationmig3_vector + populationmig4_vector)

df_combined_long<-gather(df_combined,key="key",value="Population","Population_Resident","Population_Migrant")
                           
combined_model<-ggplot(df_combined_long,aes(x=Year, y=Population, colour=key)) +
   geom_line() +ggtitle("Resident Vs Migrant species")
print(df_combined)
print(combined_model)
```

```{r}
df_ratio<-data.frame( 
  Year = year_vector,
  Population_Ratio = (populationres1_vector + populationres2_vector + populationres3_vector + populationres4_vector +populationaltmig2_vector + populationaltmig3_vector + populationaltmig4_vector)/
(populationmig1_vector+ populationmig2_vector + populationmig3_vector + populationmig4_vector))

ratio_model<-ggplot(df_ratio,aes(x=Year, y=Population_Ratio,)) +geom_line() +ggtitle("Resident/Migrant ratio") + ylim(1,2.5)
print(df_ratio)
print(ratio_model)
ggsave("ratio4.png", plot = ratio_model,width = 10,height=6)
```
